### 2015-05-27 Paper1rev3/paper1rev3.tex
updates from work
slightly better

and integrated numerically as described. By scaling an established model using a force disturbance other than our disturbance of interest, we avoided presuming the intent trajectory we hoped to recover.

>>>>

and integrated numerically as described. By scaling an established model using a force disturbance other than our disturbance of interest, we avoided presuming the intent trajectory we hoped to recover. This also serves as a test of model generalization since the training and testing data are drawn from different force disturbances. If the structure of the model is sufficiently accurate, the value of $c$ fit using data from the white noise forces will also be effective, at least initially, for the pulse force disturbances.
